Assessing Usability of Tor Browser

### 2015-04-10 PETS2015-paper/paper.tex
filler stuff

\section{Design}
In this section, we outline previous research regarding how users understand and act on the Internet, communicating relevant risks to users, and usability of Tor Browser

@@

>>>>

\section{Design}
\#STORYTIMEE  about why we chose this experiment.

Design of experiment.

Methodology of experiment.

What we hope to get from this experiment.

@@

\noindent {\bfseries 1. testing the pluggable transports} blah explain ourselves.

\noindent {\bfseries 2. censorship environments} blah explain ourselves.

\noindent {\bfseries 3. list of tasks} blah explain ourselves.

\noindent {\bfseries 4. general design feedback} (size, recruitment pool --ie general or journalists) blah explain ourselves.
